---
title: "Seroprevalence Dashboard - Date: `r format(Sys.Date(), '%b %d, %Y')`"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    social: menu
    logo: ../pics/logo.png
---

<script>
$('.navbar-logo').wrap('<a href="https://serohub.net/en/studies/" target=_blank>');
</script>

<style>                     
.navbar {
  background-color:#000075;
}
</style>     


```{r setup, include=FALSE}
knitr::opts_chunk$set(dpi = 96, fig.width = 9, fig.height = 4.5)
library(flexdashboard)
library(dplyr)
library(stringr)
library(lubridate)
library(forcats)
library(showtext)
library(ggplot2)
# Rscript.exe --encoding=UTF-8 generate_html_summary.R
font_add_google("Roboto Condensed", "robo")
showtext_auto() 

theme_set(theme_light(base_size = 24, 
                      base_family = "robo"))


recent_file <- list.files(path = "../data/", pattern = "_graphs.RData", full.names = TRUE) %>% 
  as_tibble() %>% 
  mutate(date = str_extract(value, "[0-9]{8}"),
         date = ymd(date)) %>% 
  arrange(desc(date)) %>% 
  pull(value) %>% 
  .[1]

load(recent_file) 
```


Study Details
=======================================================================


Column 
-----------------------------------------------------------------------


### Count of Participants per Study Site 

```{r fig.height=8, fig.width=8}
g01
```

Column 
-----------------------------------------------------------------------


### Seroprevalence per Study Site compared to the mean of all Sites

```{r fig.height=8, fig.width=8}
g02_map 

# knitr::include_graphics("../../01_R Scripts/g02_map.bmp")
```




Demography
=======================================================================

Column
-----------------------------------------------------------------------

### Gender distribution by age

```{r fig.height=10, fig.width=7}
g03
```


Column
-----------------------------------------------------------------------

### Probability of using homeoffice

```{r fig.width=10, fig.height=3}
g06
```



### Count of Highest Education

```{r fig.width=10, fig.height=3}
g04
```

### Count of Smoking status

```{r fig.width=10, fig.height=3}
g05
```


Seroprevalence
=======================================================================


Column
-----------------------------------------------------------------------

### Percentage of individuals tested at least once

```{r}
g07
```


### Symptomatic and Asymptomatic distribution from sero-positive individuals

```{r}
g08
```

