---
title: "Seroprevalence Dashboard - Date: `r format(Sys.Date(), '%b %d, %Y')`"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    social: menu
    logo: ../pics/logo.png
---

<script>
$('.navbar-logo').wrap('<a href="https://serohub.net/en/studies/" target=_blank>');
</script>

<style>                     
.navbar {
  background-color:#000075;
}
</style>     


```{r setup, include=FALSE}
knitr::opts_chunk$set(dpi = 96, fig.width = 9, fig.height = 4.5)
library(flexdashboard)
library(dplyr)
library(stringr)
library(lubridate)
library(forcats)
library(showtext)
library(ggplot2)
# Rscript.exe --encoding=UTF-8 generate_html_summary.R
font_add_google("Roboto Condensed", "robo")
showtext_auto() 

theme_set(theme_light(base_size = 24, 
                      base_family = "robo"))


recent_file <- list.files(path = "../data/", pattern = "_graphs.RData", full.names = TRUE) %>% 
  as_tibble() %>% 
  mutate(date = str_extract(value, "[0-9]{8}"),
         date = ymd(date)) %>% 
  arrange(desc(date)) %>% 
  pull(value) %>% 
  .[1]

load(recent_file) 
```


Study Details
=======================================================================


Column 
-----------------------------------------------------------------------


### Count of Participants per Study Site 

```{r fig.height=8, fig.width=8}
g01
```

Column 
-----------------------------------------------------------------------


### Seroprevalence per Study Site compared to the mean of all Sites

```{r fig.height=8, fig.width=8}
g02_map 

# knitr::include_graphics("../../01_R Scripts/g02_map.bmp")
```




Demography
=======================================================================

Column
-----------------------------------------------------------------------

### Gender distribution by age

```{r fig.height=10, fig.width=7}
g03
```


Column
-----------------------------------------------------------------------

### Probability of using homeoffice

```{r fig.width=10, fig.height=3}
g06
```



### Count of Highest Education

```{r fig.width=10, fig.height=3}
g04
```

### Count of Smoking status

```{r fig.width=10, fig.height=3}
g05
```


Seroprevalence
=======================================================================


Column
-----------------------------------------------------------------------

### Percentage of individuals tested at least once

```{r}
g07
```


### Symptomatic and Asymptomatic distribution from sero-positive individuals

```{r}
g08
```

Imprint
=======================================================================

**IMPRINT**  
PUBLISHER  
Helmholtz Centre for Infection Research (HZI)  
Inhoffenstraße 7 | 38124 Braunschweig  
Telefon: 0531 6181-0  
E-Mail: info@helmholtz-hzi.de  
Internet: http://www.helmholtz-hzi.de/  
  
**LEGAL FORM**  
The Helmholtz Centre for Infection Research is a Gesellschaft mit beschränkter Haftung (GmbH), which is similar to a limited liability company.
  
Commercial Register Braunschweig, Germany  
Registration Number: HRB 477  
Register court: Amtsgericht Braunschweig  
  
  
**RESPONSIBLE FOR CONTENTS:**  
Dr Stephan Glöckner, MSc  
stephan.gloeckner (at) helmholtz-hzi.de  
Telefon: 0531 6181- 3125  
  
**CORPORATE GOVERNANCE**  
The Helmholtz Centre for Infection Research GmbH submits to the “Public Corporate Governance Code (PCGC)” of the federal government according to the memorandum of association. The Code recommends that the management and the supervisory board reports on the Company’s corporate governance (Corporate Governance Report) on an annual basis.  

The report refers to the PCGK as constituted on 30th of June 2009. Management and Supervisory Board declare that the recommendations of the Code are being complied essentially and will, deviations are explained in the respective report.  

The Management Board and Supervisory Board declare that the Federal Public Corporate Governance Code as amended on 30 June 2009 has been complied with with reasonable deviations from the prescribed recommendations.  

**COPYRIGHT**  
The content of all web pages of this Internet presence is protected by copyright. All images and photos on the HZI web pages may not be copied, reproduced and distributed without the permission of the HZI, unless such action is permitted by law. Modification of the metadata (IPTC data including naming of author, source, copyright notice and terms of use) of the images is not permitted.  
  
Images under a Creative Commons License may be used according to the license used. 
  
The use of images and photographs not under a Creative Commons License is permitted in the following cases, provided the HZI is cited For editorial-journalistic publications in press and other media about the work of the HZI, for other non-commercial purposes (education, personal information). Commercial use must be requested from the HZI in advance.  

**DISCLAIMER**  
The Helmholtz Centre for Infection Research does not take any responsibility for damages that occur in connection with any use of this website. The content of this website gets reviewed and updated on a regular basis if possible, a guarantee for correctness of any content can’t be given in any case though.  
  
**INFORMATION**  
We do not take any liability for any content of any external sites we link to. The content of external sites belongs to the sphere of responsibility of it’s respective publishers.  
  
The data in this imprint is exclusively intended for getting in contact with us regarding content and legal issues. Any use of this data for advertisement is strictly prohibited.  